Yeast RNA-seq 48 sample simulation study

### 2018-07-25 datasets/RNA-Seq/yeast-simulation.Rmd
Use raw scale informative weights

  if(nDE > 0){
    # pick random set of nDE genes to add signal to
    wts <- log10(rowMeans(counts(dds_test, normalize = TRUE))+1)
    DE <- sample(1:nrow(dds_test), nDE, prob = wts)
    truth[DE] <- TRUE

>>>>

  if(nDE > 0){
    # pick random set of nDE genes to add signal to
    wts <- rowMeans(counts(dds_test, normalize = TRUE))
    DE <- sample(1:nrow(dds_test), nDE, prob = wts)
    truth[DE] <- TRUE
